%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=1in]{geometry} % Document margins
\usepackage{enumitem}
\usepackage{comment}

% Left alignment without word splitting
\usepackage[document]{ragged2e}
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\makeatletter
\newcommand \Dotfill {\leavevmode \cleaders \hb@xt@ .99em{\hss .\hss }\hfill \kern \z@}
\makeatother

\name{Jaemin Yoo} % Your name
\address{Postdoctoral Research Fellow @ Carnegie Mellon University} % Your phone number and email
\address{\textbf{Email:} jaeminyoo@snu.ac.kr \\ \textbf{Web:} jaeminyoo.github.io}

\begin{document}

%----------------------------------------------------------------------------------------
%	POSITIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Positions}

\textbf{Carnegie Mellon University}, Pittsburgh, PA, USA \hfill \emph{Mar. 2022 - Present} \\ 
Postdoctoral Research Fellow, Heinz Colledge \\
Host: Prof. Leman Akoglu

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\textbf{Seoul National University}, Seoul, South Korea \hfill \emph{Mar. 2016 - Feb. 2022} \\ 
Ph.D. in Computer Science and Engineering \\
Advisor: Prof. U Kang \\
Thesis: Probabilistic Approaches for Node and Graph Classification \\
\emph{Received the Best Ph.D. Thesis Award}

\textbf{Seoul National University}, Seoul, South Korea \hfill \emph{Mar. 2012 - Feb. 2016} \\ 
B.S. in Computer Science and Engineering

\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\smallskip
\begin{enumerate}

	\item[{[t1]}]
		Probabilistic Approaches for Node and Graph Classification \\
		\underline{Jaemin Yoo} \\
		\textbf{Ph.D. Thesis} (Best Ph.D. Thesis Award in SNU CSE)

	\item[{[c13]}]
		Model-Agnostic Augmentation for Accurate Graph Classification \\
		\underline{Jaemin Yoo}, Sooyeon Shim, and U Kang \\
		\textbf{WWW 2022} (acceptance rate 323/1822 = 17.7\%) \\

	\item[{[c12]}]
		MiDaS: Representative Sampling from Real-world Hypergraphs \\
		Minyoung Choe, \underline{Jaemin Yoo}, Geon Lee, Woonsung Baek, U Kang, and Kijung Shin \\
		\textbf{WWW 2022} (acceptance rate 323/1822 = 17.7\%) \\

	\item[{[c11]}]
		Transition Matrix Representation of Trees with Transposed Convolutions \\
		\underline{Jaemin Yoo} and Lee Sael \\
		\textbf{SDM 2022} (acceptance rate 83/298 = 27.8\%) \\

	\item[{[c10]}]
		Accurate Graph-Based PU Learning without Class Prior \\
		\underline{Jaemin Yoo}*, Junghun Kim*, Hoyoung Yoon*, Geonsoo Kim, Changwon Jang, and U Kang \\
		\textbf{ICDM 2021} (regular paper; top 98/990 = 9.9\%; *equal contribution) \\
		\emph{Selected as one of the best-ranked papers of ICDM 2021 for fast-track journal invitation}

	\item[{[c9]}]
		Accurate Multivariate Stock Movement Prediction via Data-Axis Transformer with Multi-Level Contexts  \\
		\underline{Jaemin Yoo}, Yejun Soun, Yong-chan Park, and U Kang \\
		\textbf{KDD 2021} (acceptance rate 238/1541 = 15.4\%)

	\item[{[c8]}]
		Gaussian Soft Decision Trees for Interpretable Feature-Based Classification \\
		\underline{Jaemin Yoo} and Lee Sael \\
		\textbf{PAKDD 2021} (acceptance rate 157/768 = 20.4\%)
		
	\item[{[c7]}]
		Attention-Based Autoregression for Accurate and Efficient Multivariate Time Series Forecasting \\
		\underline{Jaemin Yoo} and U Kang \\
		\textbf{SDM 2021} (acceptance rate 85/400 = 21.3\%)

	\item[{[c6]}]
		Sampling Subgraphs with Guaranteed Treewidth for Accurate and Efficient Graphical Inference \\
		\underline{Jaemin Yoo}, U Kang, Mauro Scanagatta, Giorgio Corani, and Marco Zaffalon \\
		\textbf{WSDM 2020} (acceptance rate 91/615 = 14.8\%)

	\item[{[c5]}]
		Knowledge Extraction with No Observable Data \\
		\underline{Jaemin Yoo}, Minyong Cho, Taebum Kim, and U Kang \\
		\textbf{NeurIPS 2019} (acceptance rate 1428/6743 = 21.2\%)

	\item[{[c4]}]
		EDiT: Interpreting Ensemble Models via Compact Soft Decision Trees \\
		\underline{Jaemin Yoo} and Lee Sael \\
		\textbf{ICDM 2019} (acceptance rate 194/1046 = 18.5\%)

	\item[{[c3]}]
		Belief Propagation Network for Hard Inductive Semi-Supervised Learning \\
		\underline{Jaemin Yoo}, Hyunsik Jeon, and U Kang \\
		\textbf{IJCAI 2019} (acceptance rate 850/4752 = 17.9\%)

	\item[{[c2]}]
		Fast and Scalable Distributed Loopy Belief Propagation on Real-World Graphs \\
		Saehan Jo, \underline{Jaemin Yoo}, and U Kang \\
		\textbf{WSDM 2018} (acceptance rate 83/514 = 16.3\%)

	\item[{[j1]}]
		Efficient Learning of Bounded-Treewidth Bayesian Networks from Complete and Incomplete Data Sets \\
		Mauro Scanagatta, Giorgio Corani, Marco Zaffalon, \underline{Jaemin Yoo}, and U Kang \\
		\textbf{International Journal of Approximate Reasoning}, vol. 95, pp. 152--166, 2018

	\item[{[c1]}]
		Supervised Belief Propagation: Scalable Supervised Inference on Attributed Networks \\
		\underline{Jaemin Yoo}, Saehan Jo, and U Kang \\
		\textbf{ICDM 2017} (regular paper; top 72/778 = 9.3\%)

\end{enumerate}
\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Scholarships}

Best Ph.D. Thesis Award in SNU CSE\smallskip \Dotfill \emph{Feb. 2022} \\ 
One of the Best-Ranked Papers of ICDM 2021\smallskip \Dotfill \emph{Dec. 2021} \\ 
SNU BK21 Outstanding Graduate Student Award\smallskip \Dotfill \emph{Jul. 2021} \\ 
Best Poster Award at AIIS Retreat 2021\smallskip \Dotfill \emph{Apr. 2021} \\ 
SIAM Student Travel Awards (SDM 2021) \smallskip \Dotfill \emph{Apr. 2021} \\ 
SNU BK21 Star Researcher Award \smallskip \Dotfill \emph{Feb. 2021} \\ 
Qualcomm Innovation Fellowship Korea (for Two First-Author Papers) \smallskip \Dotfill \emph{Dec. 2020} \\ 
Yulchon AI Star Award \smallskip \Dotfill \emph{Sep. 2020} \\ 
Google PhD Fellowship Program (Machine Learning) \smallskip \Dotfill \emph{Sep. 2019} \\ 
Samsung HumanTech Paper Award (Honorable Mention) \smallskip \Dotfill \emph{Feb. 2019} \\ 
Google Conference Scholarships (ICDM 2017) \smallskip \Dotfill \emph{Nov. 2017} \\ 
Paper Award in Scientific and Technical Writing by SNU \smallskip \Dotfill \emph{Jun. 2014} \\ 
Undergraduate Student Paper Award at KSC 2014 \smallskip \Dotfill \emph{Jun. 2014} \\
SNU BK21 Scholarship \smallskip \Dotfill \emph{Mar. 2019 - Aug. 2020} \\ 
Lecture \& Research Scholarship by SNU \smallskip \Dotfill \emph{Mar. 2016 - Feb. 2019} \\
National Scholarship For Science and Engineering by KOSAF \smallskip \Dotfill \emph{Mar. 2013 - Jun. 2015}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Participated Projects}

Graph-Based Gold Farming Group Detection System (NCSOFT) \smallskip \Dotfill \emph{Sep. 2020 - Feb. 2021} \\ 
Deep Learning-Based Recommender System (Wemakeprice) \smallskip \Dotfill \emph{Feb. 2019 - Dec. 2019} \\ 
Statistical Learning and Inference Method with PGMs (IDSIA) \smallskip \Dotfill \emph{Jan. 2016 - Dec. 2018} \\ 
Feature Selection Method for RNN Recommender Systems (SK Telecom) \smallskip \Dotfill \emph{Mar. 2018 - Nov. 2018} \\ 
Temporal Stock Price Prediction System (eMoney) \smallskip \Dotfill \emph{Aug. 2017 - Feb. 2018} \\ 
Video Recommender System with Multimodal Data (SK Broadband) \smallskip \Dotfill \emph{Nov. 2016 - Jun. 2017} \\ 
Distributed Machine Learning Library on Apache Spark (SK Telecom) \smallskip \Dotfill \emph{Mar. 2016 - Jan. 2017}

\end{rSection}

%----------------------------------------------------------------------------------------
%	INVITED TALKS
%----------------------------------------------------------------------------------------

\begin{rSection}{Invited Talks}

KAIST School of Electrical Engineering \smallskip \Dotfill \emph{Feb. 2022} \\ 
LG AI Research Tech Talk \smallskip \Dotfill \emph{Feb. 2022} \\ 
KAIST AI Student Colloquium \smallskip \Dotfill \emph{Oct. 2021} \\ 
SNU AI Summer School 2021 \smallskip \Dotfill \emph{Aug. 2021} \\ 
SNU AI Institute (AIIS) Retreat 2021 \smallskip \Dotfill \emph{Apr. 2021} \\ 
NAVER Online Tech Talk \smallskip \Dotfill \emph{Dec. 2020} \\ 
SNU AI Summer School 2020 \smallskip \Dotfill \emph{Aug. 2020} \\ 
SNU Hospital \smallskip \Dotfill \emph{Jul. 2020} \\ 
SNU AI Institute (AIIS) Retreat 2020 \smallskip \Dotfill \emph{Jun. 2020}\\ 
Kakao Enterprise \smallskip \Dotfill \emph{Jan. 2020} \\ 
Korea Software Congress 2019 \smallskip \Dotfill \emph{Dec. 2019} \\ 
%SNU - Samsung Research Workshop \smallskip \Dotfill \emph{Oct. 2019} \\ 
%SNU Center for AI Retreat 2019 \smallskip \Dotfill \emph{Jul. 2019} \\ 
Introduction to Data Mining @ SNU CSE \smallskip \Dotfill \emph{Jul. 2019} \\ 
Samsung Electronics \smallskip \Dotfill \emph{Mar. 2019} \\ 
Istituto Dalle Molle di Studi sull'Intelligenza Artificiale (IDSIA) \smallskip \Dotfill \emph{Jul. 2018} \\ 
Korea Software Congress 2017 \smallskip \Dotfill \emph{Dec. 2017}
%Samsung AI Forum 2017 \smallskip \Dotfill \emph{Oct. 2017}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SERVICES
%----------------------------------------------------------------------------------------

\begin{rSection}{Profesional Services}

\textbf{PC Member}
\begin{itemize}[noitemsep]
	\item KDD {\small (ACM SIGKDD Intl. Conf. on Knowledge Discovery and Data Mining)} \smallskip \Dotfill \emph{2021 - 2022}
	\item SDM {\small (SIAM International Conference on Data Mining)} \smallskip \Dotfill \emph{2022}
	\item AAAI {\small (AAAI Conference on Artificial Intelligence)} \smallskip \Dotfill \emph{2021 - 2022}
	\item BigComp {\small (IEEE International Conference on Big Data and Smart Computing)} \smallskip \Dotfill \emph{2021 - 2022}
\end{itemize}

\textbf{Journal Reviewer}
\begin{itemize}[noitemsep]
	\item Pattern Recognition \smallskip \Dotfill \emph{2021}
\end{itemize}

%\textbf{Conference Reviewer}
%\begin{itemize}[noitemsep]
%	\item ICLR \smallskip \Dotfill \emph{2021 - 2022}
%	\item NeurIPS \smallskip \Dotfill \emph{2020 - 2021}
%	\item WWW \smallskip \Dotfill \emph{2018 - 2021}
%	\item KDD \smallskip \Dotfill \emph{2018 - 2020}
%	\item BigComp \smallskip \Dotfill \emph{2017 - 2018, 2020}
%	\item CIKM \smallskip \Dotfill \emph{2017 - 2019}
%	\item WSDM \smallskip \Dotfill \emph{2019}
%	\item ICDM \smallskip \Dotfill \emph{2018}
%	\item SAC \smallskip \Dotfill \emph{2018}
%\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{comment}
\begin{rSection}{Working Experience}

\textbf{Infosys Limited} (Bengaluru, India) \hfill \emph{Jun. 2015 - Jul. 2015} \\ 
Student Intern \\
Project: \emph{Prediction of CPU and memory usage in cloud services}

\textbf{SK Hynix} (Incheon, South Korea) \hfill \emph{Dec. 2014 - Jan. 2015} \\ 
Student Intern \\
Project: \emph{Documentation and improvement of SSD controller systems}

\textbf{KISTI} (Daejeon, South Korea) \hfill \emph{Jan. 2014 - Feb. 2014} \\ 
Student Intern \\
Project: \emph{Exploiting HTCaaS for traffic simulation}

\end{rSection}
\end{comment}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}

\textbf{Teaching Assistant} (Seoul National University)
\begin{itemize}[noitemsep]
	\item Large Data Analysis (M1522.000900, 002) \smallskip \Dotfill \emph{Fall 2017}
	\item Introduction to Data Mining (M1522.001400\_001) \smallskip \Dotfill \emph{Spring 2017}
	\item Data Structures (M1522.001600\_002) \Dotfill \emph{Fall 2016}
\end{itemize}

\textbf{Teaching Assistant} (Other Organizations)
\begin{itemize}[noitemsep]
	\item Deep Learning, Samsung Electronics \smallskip \Dotfill \emph{Apr. 2018 - Feb. 2019}
	\item Deep Learning, SNU Fourth Industrial Revolution Academy \smallskip \Dotfill \emph{Oct. 2017 - Dec. 2018}
	\item Distributed Computing, SNU Big Data Academy \smallskip \Dotfill \emph{Feb. 2017 - Dec. 2017}
	\item Distributed Computing, SNU Big Camp \smallskip \Dotfill \emph{Aug. 2016 - Feb. 2017}
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PATENTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Patents}
\smallskip
\begin{enumerate}

	\item \underline{Jaemin Yoo} and U Kang, ``Apparatus and Method for Classifying Nodes", KR-Registration No. 10-1924832 (2018)
		
	\item Taebum Kim, \underline{Jaemin Yoo}, and U Kang, ``Method for Compressing Deep Learning Neural Networks and Apparatus for Performing the Same", KR-Registration No. 10-2199285 (2020)

	\item \underline{Jaemin Yoo} and U Kang, ``Method for Extracting Knowledge from Artificial Neural Network and Apparatus for Performing the Same", KR-Registration No. 10-2345262 (2021)
		
	\item \underline{Jaemin Yoo}, Sooyeon Shim, and U Kang, ``Apparatus and Method for Data Augmentation", KR-Application No. 10-2021-0169909 (2021)
		
	\item \underline{Jaemin Yoo}, Hyunsik Jeon, Jinhong Jung, and U Kang, ``Apparatus and Method for Predicting Feature of Node", KR-Application No. 10-2021-0172385 (2021)

\end{enumerate}
\end{rSection}

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------

\end{document}
